---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The `nzmigration` R package contains a single dataset,
`nz_internal_migration_summary`, of summary statistics about internal migration
in New Zealand from the 2013 census, from the [Spreadsheet
File](http://m.stats.govt.nz/browse_for_stats/population/Migration/internal-migration/tables.aspx)
published by Statistics New Zealand.

This is not an official package of the New Zealand government and is not
associated with the New Zealand government in any way.

The data was extracted from the spreadsheet by using the
[tidyxl](https://nacnudus.github.io/tidyxl) and
[unpivotr](https://nacnudus.github.io/unpivotr) packages.

## Installation

You can install nzmigration from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("nacnudus/nzmigration")
```

## Example

```{r example}
library(nzmigration)
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(scales))

nz_internal_migration_summary %>%
  filter(table == "Table18",
         var2 == "People of MÄori Ethnicity",
         var3 == "Total",
         var5 == "Total",
         var6 != "Total") %>%
  separate(var6, c("age", "year"), sep = " ", extra = "drop") %>%
  select(-year) %>%
  select(var4, age, count) %>%
  spread(var4, count) %>%
  mutate_at(-1, `/`, .$Total) %>%
  select(-Total) %>%
  gather(var4, percent, -age) %>%
  ggplot(aes(age, percent)) +
  geom_bar(stat = "identity") +
  facet_wrap(~var4, scales = "free_y") +
  scale_y_continuous(labels = percent)
```
